---
title: "Lab11"
output: html_document
date: "2024-05-17"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```
```{r}
X <- c(1,4,3,2,5,4,3,6,7,8)
Y <- c(1,3,6,7,8,2,8,7,6,9)
```


1. An X and Y variable contain the above numbers.

   A. Compute Pearson's $r$ and report the associated p-value using the `cor.test()` function. (2 points)

   B. Use a permutation test to create a null-distribution, and report the p-value for getting the observed correlation or larger using your simulated null-distribution. (2 points)

```{r}
cor(X, Y)
cor.test(X, Y)$p.value

Rs <- replicate(10000, cor(sample(X), sample(Y)))
mean(Rs >= cor(X, Y))
```


2. Using the variables X and Y above, and assuming that the values could be re-ordered in any way, report the following:

   A. the smallest possible sum of cross-products (1 point)

   B. the largest possible sum of cross-products (1 point)

```{r}
# smallest
sum(sort(X) * sort(Y, decreasing = TRUE))
# largest
sum(sort(X) * sort(Y))
```

