---
title: "Lab8"
output: html_document
date: "2024-05-10"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(tidyverse)
```
1. Write a function to convert a vector of raw-scores into z-scores. The function should have inputs for the vector, the mean and sd of the normal distribution, and should return a vector of zscores. (1 point). Also, demonstrate that the function works correctly (1 point). How you make the demonstration is up to you.   

* Advanced: Have an option so that the function will convert the raw scores to zscores in one of two ways:  

  + using user provided mean and standard deviation  

  + using the calculated mean and standard deviation from the raw scores  

```{r}
zscore_convert <- function(score, mean = NULL, sd = NULL){
  Mean <- ifelse(is.null(mean), mean(score), mean)
  SD <- ifelse(is.null(sd), sd(score), sd)
  (score - Mean)/SD
}
scores <- rnorm(1000, 100, 15)
mean_scores <- mean(scores)
sd_scores <- sd(scores)
std_scores <- zscore_convert(scores)

identical(sum(scores > mean_scores & scores < mean_scores + sd_scores),
          sum(std_scores > 0 & std_scores < 1))
identical(sum(scores > mean_scores + sd_scores & scores < mean_scores + 2*sd_scores),
          sum(std_scores > 1 & std_scores < 2))
identical(sum(scores > mean_scores + 2*sd_scores & scores < mean_scores + 3*sd_scores),
          sum(std_scores > 2 & std_scores < 3))

v <- seq(-10, 10, 2)
zscore_convert(v, 10, 2)
```
2. Base R does not have a function for a z-test. Write a function to accomplish a one-sample z-test. Remember, a one-sample z test is used to compare the probability of obtaining the sample mean (or larger or smaller) if it came from a known normal distribution. (2 points)
* Use your z-test function to conduct a test of the following. A sample of 25 scores is taken. The mean of the sample is 50. The sample is assumed to have been taken from a normal distribution with mean 40 and standard deviation 7. Report a one-tailed z-test, examining the probability of obtaining a sample of greater than 50 in this situation. Report the results, and give a brief sentence explaining the result and the inference you make (2 points).

```{r}
z_test <- function(smean, n, pmean, psd){
  p_value <- ifelse(smean > pmean,
              pnorm(smean, pmean, psd/sqrt(n), lower.tail = FALSE),
              pnorm(smean, pmean, psd/sqrt(n)))
  return(cat("The p_value of the one-tailed z-test is", p_value))
}
z_test(50, 25, 40, 7)

```
  + *As the result of our z_test reveals, the p_value is very small indicating that the probability of obtaining a sample of 25 values with mean 50 or higher for the given normal population is really low.*

