---
title: "Lab9"
output: html_document
date: "2024-05-12"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(tidyverse)
library(readxl)
```
1. The following paper links to open data, and describes a design where two chi-square tests are performed for Experiment 1 (A copy of this paper will be made available).   

Silver, A. M., Stahl, A. E., Loiotile, R., Smith-Flores, A. S., & Feigenson, L. (2020). When Not Choosing Leads to Not Liking: Choice-Induced Preference in Infancy. Psychological Science, 0956797620954491.   

Obtain the data from the online repository, show your code for loading it into R, then conduct the same tests reported in Experiment 1 that the authors conducted. These include one binomial test, and two chi-square tests. Briefly report your re-analysis, and discuss whether you obtained the same values as the authors did (6 points).   

```{r}
When_not_choosing_leads_to_not_liking_Data <- read_excel("data/When not choosing leads to not liking_Data.xlsx")
exp1 <- When_not_choosing_leads_to_not_liking_Data |> filter(ExperimentNumber == 1)
binom.test(sum(exp1$`Infant Chose C`), 
           n = length(exp1$`Infant Chose C`),
           alternative = "two.sided")
age_t1 <- table(exp1 |> select(AgeMonths, `Infant Chose C`))
age_m1 <- matrix(age_t1, nrow = 20)
chisq.test(age_m1)
gender_t1 <- table(exp1 |> select(Gender, `Infant Chose C`))
gender_m1 <- gender_t1 |> matrix(nrow = 2)
chisq.test(gender_m1)
```
*I think the continuity correction should be applied in this situation but to replicate the paper's results, I will set it off.*
```{r}
chisq.test(gender_m1, correct = FALSE)
```

